\textsc{TheHaloMod}: An online calculator for the halo model

### 2020-09-28 paper.tex
change some tables to use tabular
add some more refs
fix Bosch ref

\usepackage{xcolor}
\usepackage{lineno}
\usepackage[colorlinks=true,urlcolor=black,linkcolor=blue,citecolor=blue]{hyperref}
\usepackage{minted}
\usepackage{longtable,booktabs,tabu}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{pbox}
\usepackage{amssymb}
\usepackage{layouts}
\usepackage{subfig}
\usepackage{microtype}
%\usepackage{subcaption}
%\usepackage{graphicx}

@@

First, NFW suggested that concentration is intimately related to the assembly history of halos, which can be summarized as their age or formation time. Physically, this dependence can be understood by the transition from the fast to the slow accretion regime, after which the halo boundary (and its concentration) grow mostly via pseudo-evolution while the scale radius remains more or less constant \citep{Navarro1997, Bullock2001, Vandenbosch2002, Wechsler2002, Zhao2003, Dalal2010, Diemer2013, Ludlow2013, Wang2020}. This logic has motivated numerous models based on some quantification of the age of halos \citep[e.g.,][]{Eke2001, Zhao2009, Giocoli2012, Ludlow2014, Ludlow2016, Correa2015b}.

@@

\begin{tabu}{X[1.4l]X[1.2l]X[2.6l]X[1.9l]X[0.6l]}
\toprule[0.05cm]
 \textsc{Ref} & \textsc{Name} & \textsc{Formula} & \textsc{Params} & \textsc{hmf}\\
 \toprule[0.05cm]

@@

\citet{Seljak2004} & \texttt{Seljak04} & $\displaystyle a + bx^c + \frac{d}{ex+1} + fx^g$ & $x=m/M_\star$, $a=0.53$, $b=0.39$, $c=0.45$, $d=0.13$, $e=40$, $f=5\times10^{-4}$, $g=1.5$ & \\
\midrule
\citet{Seljak2004} & \texttt{Seljak04Cosmo} & $\displaystyle b_\text{Sel} + \log_{10}x \left[a_1(\Omega'_m + n'_s) + a_2(\sigma'_8 + h')\right]$ & $a_1 = 0.4$, $a_2=0.3$ $\Omega'_m=\Omega_m-0.3$, $n'_s = n_s-1$, $\sigma'_8 = \sigma_8-0.9$, $h' = h-0.7$& \\
\midrule
\citet{Pillepich2010} & \texttt{Pillepich10} & $\displaystyle B_0 + B_1\sqrt{\nu} + B_2\nu$ & $B_0=0.647$, $B_1=-0.320$, $B_2=0.568$ & \\
\midrule
 \citet{Tinker2010} & \texttt{Tinker10} & $\displaystyle 1 - A\frac{\nu^{a/2}}{\nu^{a/2} + \delta_c^a} + B\nu^{b/2} + C\nu^{c/2}$ & $A=1+0.24y\exp[-(4/y)^4]$, $a = 0.44 y - 0.88$, $B = 0.183$, $b = 1.5$, $C = 0.019+0.107y+0.19\exp[-(4/y)^4]$, $c = 2.4$, $y=\log_{10}\Delta_h$. &  \\
 \midrule
 \citet{Tinker2010} & \texttt{Tinker10PBsplit} & $\displaystyle 1 + \frac{\gamma\nu-(1+2\eta)}{\delta_c} + \frac{2\phi/\delta_c}{1+(\beta^2\nu)^\phi}$ & Same as $f_\text{Tinker10}$ & \texttt{Tinker10} \\
 \midrule
 & \texttt{UnityBias} & $b(\nu) = 1$ & & \\
 \bottomrule[0.05cm]
 \end{tabu}
 \caption[Summary of included \texttt{Bias} models]{Summary of included \texttt{Bias} models. Note that the fit of \texttt{Manera10} is dependent on Friends-of-Friends linking length and redshift, and we give the result for $l = 0.2$ at $z=0$.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{onecolumn}
\begingroup
\small
\begin{table*} 
\begin{tabu}{X[1l]X[3.5l]} 
\toprule[0.05cm]
\textsc{Name \& Refs.} & \textsc{Formulae} \\
\midrule[0.05cm]
\texttt{NFW} & $\displaystyle f(x) = x^{-1}(1+x)^{-2}$ \\
\citet{Navarro1997} & $\displaystyle  h(c) = \frac{c}{1+c} + \ln(1+c)$ \\
\citet{Sheth2001a} & $\displaystyle    p(\kappa,c) = \cos (\kappa) \left(\text{Ci}(c \kappa+\kappa)-\text{Ci}(\kappa)\right) 
                   +\sin (\kappa) \left(\text{Si}(c \kappa+\kappa)-\text{Si}(\kappa)\right)-\frac{\sin (c \kappa)}{c \kappa+\kappa}$ \\
\citet{Ma2000} & $\displaystyle    p(\kappa) =  \frac{1}{2} \left[(\pi -2 \text{Si}|\kappa|) \sin|\kappa|-2 \cos (\kappa) \text{Ci}| \kappa| \right]$ \\
& $\displaystyle  l(x,c) = 4\pi \begin{cases} (T_1 + T_2 +T_3) & 0\leq x \leq c \\
 	(T_4 + T_5) & c\leq x \leq 2c \end{cases}$ \\
 & $\displaystyle l(x) = \frac{8\pi}{x^2(x+2)}\left[\frac{(x^2+2x+2)\ln(1+x)}{x(x+2)} -1 \right]$ \\
 \midrule

@@

\texttt{Hernquist}   & $\displaystyle f(x) = \frac{1}{x(1+x)^3}$ \\
  \citet{Hernquist1990} & $\displaystyle  h(c) = \frac{c^2}{2(1+c)^2}$ \\
\citet{Sheth2001a} & $\displaystyle   p(\kappa) = \frac{1}{4} \left[-|\kappa| (2 \text{Ci}|\kappa| \sin|\kappa|+\pi\cos(\kappa)) \right.
    \left.+2\kappa \text{Si}(\kappa) \cos (\kappa)+2\right]$ \\ 
  & $\displaystyle p(\kappa,c) =  1/2 - \frac{\sin (c \kappa)+(c+1)
   \kappa \cos (c \kappa)}{2\kappa(c+1)^2} 
   + \frac{k}{2} \left[\sin (\kappa) (\text{Ci}(c \kappa+\kappa)-\text{Ci}(\kappa)) \right.
   \left. +\cos (\kappa) (\text{Si}(\kappa)-\text{Si}(c \kappa+\kappa))\right] $\\
  & $\displaystyle  l(x) = \frac{16\pi(h_1 - h_2)}{x^4 * (2 + x)^4} $\\
  & $\displaystyle  h_1(x) = \frac{24 + 60 x + 56 x ^2 + 24x^3 + 6x^4 + x^5}{1 + x} $ \\
  & $\displaystyle  h_2(x) = 12(1 + x)(2 + 2x + x^2)\ln(1 + x) / x$ \\
 \midrule

@@

\bottomrule[0.05cm]
\end{tabu}
\caption[Summary of included \texttt{Profile} models]{Summary of included \texttt{Profile} models. Note that for $p$ and $l$, functions explicitly including $c$ are the usual profiles truncated at $r_\Delta$, whereas those that do not explicitly include $c$ are not truncated (these are rather unhelpful in terms of the HM). $G$ is the Meijer-$G$ function. The functions $T_i$ in the NFW definition are found in the text, Eq. \ref{eq:nfw_t}.}
\label{tab:models_profile}
\end{table*}

@@

\bibliography{library, mybibfile}

>>>>

\usepackage{array}
\usepackage{lineno}
\usepackage{xcolor}
\usepackage{lineno}
\usepackage[colorlinks=true,urlcolor=black,linkcolor=blue,citecolor=blue]{hyperref}
\usepackage{minted}
\usepackage{longtable,booktabs,tabu}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{pbox}
\usepackage{amssymb}
\usepackage{layouts}
\usepackage{subfig}
\usepackage{microtype}

@@

First, NFW suggested that concentration is intimately related to the assembly history of halos, which can be summarized as their age or formation time. Physically, this dependence can be understood by the transition from the fast to the slow accretion regime, after which the halo boundary (and its concentration) grow mostly via pseudo-evolution while the scale radius remains more or less constant \citep{Navarro1997, Bullock2001, B2, Wechsler2002, Zhao2003, Dalal2010, Diemer2013, Ludlow2013, Wang2020}. This logic has motivated numerous models based on some quantification of the age of halos \citep[e.g.,][]{Eke2001, Zhao2009, Giocoli2012, Ludlow2014, Ludlow2016, Correa2015b}.

@@

\begin{tabular}{>{\raggedright}m{3cm} >{\raggedright}m{2.6cm} >{\raggedright}m{5.2cm} >{\raggedright\arraybackslash}m{4.2cm} >{\raggedright\arraybackslash}m{1.2cm}}
\toprule
 \textsc{Ref} & \textsc{Name} & \textsc{Formula} & \textsc{Params} & \textsc{hmf}\\
\toprule

@@

\citet{Seljak2004} & \texttt{Seljak04} & $\displaystyle a + bx^c + \frac{d}{ex+1} + fx^g$ & $x=m/M_\star$, $a=0.53$, $b=0.39$, $c=0.45$, $d=0.13$, $e=40$, $f=5\times10^{-4}$, $g=1.5$ & \\
\midrule
\citet{Seljak2004} & \texttt{Seljak04Cosmo} & $\displaystyle b_\text{Sel} + \log_{10}x \left[a_1(\Omega'_m + n'_s) + a_2(\sigma'_8 + h')\right]$ & $a_1 = 0.4$, $a_2=0.3$ $\Omega'_m=\Omega_m-0.3$, $n'_s = n_s-1$, $\sigma'_8 = \sigma_8-0.9$, $h' = h-0.7$& \\
\midrule
\citet{Pillepich2010} & \texttt{Pillepich10} & $\displaystyle B_0 + B_1\sqrt{\nu} + B_2\nu$ & $B_0=0.647$, $B_1=-0.320$, $B_2=0.568$ & \\
\midrule
 \citet{Tinker2010} & \texttt{Tinker10} & $\displaystyle 1 - A\frac{\nu^{a/2}}{\nu^{a/2} + \delta_c^a} + B\nu^{b/2} + C\nu^{c/2}$ & $A=1+0.24y\exp[-(4/y)^4]$, $a = 0.44 y - 0.88$, $B = 0.183$, $b = 1.5$, $C = 0.019+0.107y+0.19\exp[-(4/y)^4]$, $c = 2.4$, $y=\log_{10}\Delta_h$. &  \\
 \midrule
 \citet{Tinker2010} & \texttt{Tinker10PBsplit} & $\displaystyle 1 + \frac{\gamma\nu-(1+2\eta)}{\delta_c} + \frac{2\phi/\delta_c}{1+(\beta^2\nu)^\phi}$ & Same as $f_\text{Tinker10}$ & \texttt{Tinker10} \\
 \midrule
 & \texttt{UnityBias} & $b(\nu) = 1$ & & \\
 \bottomrule
 \end{tabular}
 \caption[Summary of included \texttt{Bias} models]{Summary of included \texttt{Bias} models. Note that the fit of \texttt{Manera10} is dependent on Friends-of-Friends linking length and redshift, and we give the result for $l = 0.2$ at $z=0$.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begingroup
\small
\begin{table*} 
\begin{tabular}{ m{4cm} m{12cm}} 
\toprule
\textsc{Name \& Refs.} & \textsc{Formulae} \\
\toprule
\texttt{NFW} & $\displaystyle f(x) = x^{-1}(1+x)^{-2}$ \\
\citet{Navarro1997} & $\displaystyle  h(c) = \frac{c}{1+c} + \ln(1+c)$ \\
\citet{Sheth2001a} & $\displaystyle    p(\kappa,c) = \cos (\kappa) \left(\text{Ci}(c \kappa+\kappa)-\text{Ci}(\kappa)\right) 
                   +\sin (\kappa) \left(\text{Si}(c \kappa+\kappa)-\text{Si}(\kappa)\right)-\frac{\sin (c \kappa)}{c \kappa+\kappa}$ \\
\citet{Ma2000} & $\displaystyle    p(\kappa) =  \frac{1}{2} \left[(\pi -2 \text{Si}|\kappa|) \sin|\kappa|-2 \cos (\kappa) \text{Ci}| \kappa| \right]$ \\
& $\displaystyle  l(x,c) = 4\pi \begin{cases} (T_1 + T_2 +T_3) & 0\leq x \leq c \\
 	(T_4 + T_5) & c\leq x \leq 2c \end{cases}$ \\
 & $\displaystyle l(x) = \frac{8\pi}{x^2(x+2)}\left[\frac{(x^2+2x+2)\ln(1+x)}{x(x+2)} -1 \right]$ \\
 \midrule

@@

\texttt{Hernquist}   & $\displaystyle f(x) = \frac{1}{x(1+x)^3}$ \\
  \citet{Hernquist1990} & $\displaystyle  h(c) = \frac{c^2}{2(1+c)^2}$ \\
\citet{Sheth2001a} & $\displaystyle   p(\kappa) = \frac{1}{4} \left[-|\kappa| (2 \text{Ci}|\kappa| \sin|\kappa|+\pi\cos(\kappa)) \right.
    \left.+2\kappa \text{Si}(\kappa) \cos (\kappa)+2\right]$ \\ 
  & $\displaystyle p(\kappa,c) =  1/2 - \frac{\sin (c \kappa)+(c+1)
   \kappa \cos (c \kappa)}{2\kappa(c+1)^2} $ \\
& $\displaystyle \ \ \ \ \ \ \ \ \ 
   + \frac{k}{2} \left[\sin (\kappa) (\text{Ci}(c \kappa+\kappa)-\text{Ci}(\kappa)) \right.
   \left. +\cos (\kappa) (\text{Si}(\kappa)-\text{Si}(c \kappa+\kappa))\right] $\\
  & $\displaystyle  l(x) = \frac{16\pi(h_1 - h_2)}{x^4 * (2 + x)^4} $\\
  & $\displaystyle  h_1(x) = \frac{24 + 60 x + 56 x ^2 + 24x^3 + 6x^4 + x^5}{1 + x} $ \\
  & $\displaystyle  h_2(x) = 12(1 + x)(2 + 2x + x^2)\ln(1 + x) / x$ \\
 \midrule

@@

\bottomrule
\end{tabular}
\caption[Summary of included \texttt{Profile} models]{Summary of included \texttt{Profile} models. Note that for $p$ and $l$, functions explicitly including $c$ are the usual profiles truncated at $r_\Delta$, whereas those that do not explicitly include $c$ are not truncated (these are rather unhelpful in terms of the HM). $G$ is the Meijer-$G$ function. The functions $T_i$ in the NFW definition are found in the text, Eq. \ref{eq:nfw_t}.}
\label{tab:models_profile}
\end{table*}

@@

\bibliography{library}
